### 2022-10-31 chapters/background.tex
minor edits

>>>>

\blue{The complexity $ \bncomplexity(\graph) $ of a Bayesian network $ (\graph, \theta) $ with discrete random variables $ \graphvertices $ is defined as the number of independent parameters used to define the probability distribution of $ \graphvertices $~\cite{murakonda2021quantifying}. Let $ \bnnumdiscrete(\graphvertex) $ denote the number of distinct values that a random variable $ \graphvertex $ can take. As such, for each conditional probability $ \Pr[\graphvertex_i = v_i | \parent(\graphvertex_i) = \mathbf{u}; \theta] $, we need $ \bnnumdiscrete(\parent(\graphvertex_i))(\bnnumdiscrete(\graphvertex_i) - 1) $ independent parameters. Thus, the total complexity of a Bayesian network is:}

\blue{
\begin{align}
	\bncomplexity(\graph) = \sum_{i=1}^{|\graphvertices|} \bnnumdiscrete(\parent(\graphvertex_i))(\bnnumdiscrete(\graphvertex_i) - 1)
\end{align}
}

### 2022-10-31 chapters/interpretability/imli/introduction.tex
minor edits

\vspace{1em}
\boxed{
\begin{array}{rl}
	& \text{A tumor is malignant if}\\
	&[(\text{compactness SE} < 0.1) \text{\textbf{ OR }}  \neg (0.1 \le \text{concave points} < 0.2)]
	\text{\textbf{ \blue{AND} }} \\
	&[\neg (0.2 \le \text{area} < 0.3) \text{\textbf{ OR }} \neg (0.1 \le \text{largest symmetry }< 0.2)]
	\text{\textbf{ \blue{AND} }} \\
	&[(0.6 \le \text{compactness} < 0.7) \text{\textbf{ OR }} (0.4 \le \text{concave points} < 0.5) \text{\textbf{ OR }}  (\text{area SE} \ge 0.1)\\
	& \text{\textbf{ OR }} (0.3 \le \text{largest concavity} < 0.4) \text{\textbf{ OR }} (0.2 \le \text{largest area} < 0.3)]
\end{array}
}
\vspace{1em}

\begin{example}
	\normalfont
	We learn an interpretable classification rule in CNF for predicting the classification of a tumor cell. We consider WDBC (Wisconsin Diagnostic Breast Cancer) dataset~\cite{agarap2018breast} to learn a CNF formula with three \emph{clauses} and nine Boolean \emph{literals}. In the formula, clauses are connected by Boolean `AND', where each clause contains \emph{literals} connected by Boolean `OR'. Informally, a tumor cell is malignant if at least one literal in each clause becomes true.
\end{example}

>>>>

\vspace{1em}
\boxed{
\begin{array}{rl}
	& \text{A tumor is malignant if}\\
	&[(\text{compactness SE} < 0.1) \text{\textbf{ OR }}  \neg (0.1 \le \text{concave points} < 0.2)]
	\text{\textbf{ \blue{AND} }} \\
	&[\neg (0.2 \le \text{area} < 0.3) \text{\textbf{ OR }} \neg (0.1 \le \text{largest symmetry }< 0.2)]
\end{array}
}
\vspace{1em}

\begin{example}
	\normalfont
	\blue{We learn an interpretable classification rule in CNF for predicting the classification of a tumor cell. We consider WDBC (Wisconsin Diagnostic Breast Cancer) dataset~\cite{agarap2018breast} to learn a CNF formula with two \emph{clauses} and four Boolean \emph{literals}. In the formula, clauses are connected by Boolean `AND', where each clause contains \emph{literals} connected by Boolean `OR'. Informally, a tumor cell is malignant if at least one literal in each clause becomes true.}
\end{example}
